Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-27 thesis/chapters/ch_chapter4.tex
more writing

At the beginning of each restart, we place by-hand one or more enrichment events at assigned positions throughout the galaxy, with thermal injection energies ($E_{\rm ej}$), masses ($m_{\rm ej}$), and metal fractions ($Z_{\rm ej}$). We note that the injection masses, particularly the metal fractions, are somewhat arbitrary as they are likely dynamically insigificant relative to the ambient ISM mass in which they occur. The important parameter here is $E_{\rm ej}$, which we vary to sample the range of ejection energies associated with significant sources of chemical enrichment, including AGB winds ($10^{46}$~erg)\footnote{Assuming full thermalization of the total mechanical energy output of an AGB wind.}, NS-NS mergers ($10^{49} - 10^{50}$~erg), supernovae (10$^{51}$~erg), and exotic enrichment sources, such as hypernovae, that can reach much higher energies (10$^{52}$~erg). Each run contains only sources from a single event type, as indicated in the run-name by the log of the injection energy in ergs. For example, the run beginning at 180~Myr with AGB-like events is labelled ``II_E46". The metal enrichment from each source is tracked and evolved with a unique passive scalar tied to the individual source and separate from any additional chemical enrichement that may occur within the galaxy over time.

@@

Perhaps the three most important paramters to quantify for each enrichment event are: 1) what fraction of released metals are immediately available for star formation, 2) what fraction of metals are carried out of the galaxy in outflows, and 3) how and over what timescale do metals cool from hot phases into star forming gas. We discuss each of these points in Section~\ref{ch4:sec:ISM CGM}. In Section~\ref{ch4:sec:spreads} we go further and address the relative homogeneity of the metals retained by the ISM for each enrichment source.

@@

We summarize the source-averaged results for all enrichment events in runs II_E46, II_E49, II_E50, II_E51, and II_E52 in Figure~\ref{ch4:fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid). These plots show a clear, immediate trend across $E_{\rm ej}$ for all lines in the figure, but the differences are most striking for the ISM (black, solid), CGM (black, dashed) lines.

>>>>

At the beginning of each restart, we place by-hand one or more enrichment events at assigned positions throughout the galaxy, with thermal injection energies ($E_{\rm ej}$), masses ($m_{\rm ej}$), and metal fractions ($Z_{\rm ej}$). We note that the injection masses, particularly the metal fractions, are somewhat arbitrary as they are likely dynamically insignificant relative to the ambient ISM mass in which they occur. The important parameter here is $E_{\rm ej}$, which we vary to sample the range of ejection energies associated with significant sources of chemical enrichment, including AGB winds ($10^{46}$~erg)\footnote{Assuming full thermalization of the total mechanical energy output of an AGB wind.}, NS-NS mergers ($10^{49} - 10^{50}$~erg), supernovae (10$^{51}$~erg), and exotic enrichment sources, such as hypernovae, that can reach much higher energies (10$^{52}$~erg). Each run contains only sources from a single event type, as indicated in the run-name by the log of the injection energy in ergs. For example, the run beginning at 180~Myr with AGB-like events is labeled ``II\_E46". The metal enrichment from each source is tracked and evolved with a unique passive scalar tied to the individual source and separate from any additional chemical enrichment that may occur within the galaxy over time.

@@

Perhaps the three most important parameters to quantify for each enrichment event are: 1) what fraction of released metals are immediately available for star formation, 2) what fraction of metals are carried out of the galaxy in outflows, and 3) how and over what timescale do metals cool from hot phases into star forming gas. We discuss each of these points in Section~\ref{ch4:sec:ISM CGM}. In Section~\ref{ch4:sec:spreads} we go further and address the relative homogeneity of the metals retained by the ISM for each enrichment source.

@@

We summarize the source-averaged results for all enrichment events in runs II\_E46, II\_E49, II\_E50, II\_E51, and II\_E52 in Figure~\ref{ch4:fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid). These plots show a clear, immediate trend across $E_{\rm ej}$ for all lines in the figure, but the differences are most striking for the ISM (black, solid), CGM (black, dashed) lines. In Chapter~\ref{ch:chapter3}
% \citep{Emerick2019}
we demonstrated that there was a significant difference in metal ejection fraction, $f_{\rm ej}$, for metals from AGB sources as compared to metals released in SNe. Here, we confirm that this is driven predominantly by differences in the energy of the events, and not necessarily when or where they occur in the ISM. The clear trend in Figure~\ref{ch4:fig:ISM_CGM} shows that events with higher $E_{\rm ej}$ are much more readily ejected from the disk of the galaxy, while events with lower $E_{\rm ej}$ couple poorly to the same galactic outflows.
\textit{statement on how immediate enrichement is after events}
% By 10~Myr after the enrichment events,
The high-energy events rapidly converge on a peak $f_{\rm ej}$ within about 20~Myr of the event, with only a gradual increase towards the end of the 150~Myr as the metals in the ISM are swept up in additional outflows. The lower energy events evolve more gradually. The lowest energy event, corresponding to AGB winds, reaches $f_{\rm ej}$ ~ 0.68, which increases to 0.87 for the 10$^{51}$~erg events, and 0.95 for the 10$^{52}$~erg event. This implies that, if one to were assume that all metals behaved the same and adopted an $f_{\rm ej}$ of $\sim$0.9, typical of SNe-like events (and which is comparable to that observed for O in Local Group dwarf galaxies, \citep{Kirby2011,McQuinn2015}), one would underestimate the amount of AGB metals in the ISM by a factor of $\sim$ 3, and overestimate exotic, high-energy sources by a factor of $\sim$2.
% This ejection fraction is a critical ingredient in chemical evolution models, and the fact that it varies with enrichment source can

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{figures/ch4/AGB1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/NSNS1_enrichment_evolution_average_CGM} \\
\includegraphics[width=0.45\linewidth]{figures/ch4/SNE1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
\caption{Time evolution of the }
\label{fig:ch4:ISM_CGM}
\end{figure*}

% make a figure here showing JUST the CNM evolution of the ISM for each source
